---
title: "F1"
editor: visual
---

```{r}
library(f1dataR)
library(dplyr)
library(ggplot2)


```

```{r}
# f1dataR::get_session_drivers_and_teams(2024, 16, session = "R")

```

```{r}
library(ggplot2)
# Load the data
results <- load_results(2020, 1) %>%
  mutate(
    grid = as.numeric(grid),
    position = as.numeric(position)
  )

ggplot(results, aes(x = position, y = grid)) +
  geom_point(color = "white") +
  stat_smooth(method = "lm") +
  theme_dark_f1(axis_marks = TRUE) +
  ggtitle("2020 Austrian Grand Prix Grid - Finish Position") +
  xlab("Finish Position") +
  ylab("Grid Position")

```

```{r}
# lec <- load_driver_telemetry(2024, 1, "Q", driver = "LEC", laps = "fastest")
# ham <- load_driver_telemetry(2024, 1, "Q", driver = "HAM", laps = "fastest")
# per <- load_driver_telemetry(2024, 1, "Q", driver = "PER", laps = "fastest")
# 
# telem <- bind_rows(lec, ham, per) %>%
#   select(rpm, speed, n_gear, throttle, brake, drs, distance, time, driver_code) %>%
#   mutate(drs = ifelse(drs == 12, 1, 0))
# 
# drivercolours <- c(
#   "LEC" = get_driver_color("LEC", 2022, 1),
#   "HAM" = get_driver_color("HAM", 2022, 1),
#   "PER" = get_driver_color("PER", 2022, 1)
# )
```

# Chapter 3.6 Glossary

This chapter provides a list of common terms and definitions related to
data types, R programming, and research methods. Understanding these
terms is essential for working effectively with data and code in R
Markdown.

## Glossary of Terms

| **Term**          | **Definition**                                                                                                                                                                        |
|-------------------|---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| **argument**      | A variable that provides input to a function.                                                                                                                                         |
| **categorical**   | Data that can only take certain values, such as types of pet.                                                                                                                         |
| **character**     | A data type representing strings of text.                                                                                                                                             |
| **chunk**         | A section of code in an R Markdown file.                                                                                                                                              |
| **continuous**    | Data that can take on any values between other existing values.                                                                                                                       |
| **data type**     | The kind of data represented by an object.                                                                                                                                            |
| **default value** | A value that a function uses for an argument if it is skipped.                                                                                                                        |
| **double**        | A data type representing a real decimal number.                                                                                                                                       |
| **factor**        | A data type where a specific set of values are stored with labels; An explanatory variable manipulated by the experimenter.                                                           |
| **geom**          | The geometric style in which data are displayed, such as boxplot, density, or histogram.                                                                                              |
| **integer**       | A data type representing whole numbers.                                                                                                                                               |
| **knit**          | To create an HTML, PDF, or Word document from an R Markdown (Rmd) document.                                                                                                           |
| **likert**        | A rating scale with a small number of discrete points in order.                                                                                                                       |
| **logical**       | A data type representing TRUE or FALSE values.                                                                                                                                        |
| **median**        | The middle number in a distribution where half of the values are larger and half are smaller.                                                                                         |
| **nominal**       | Categorical variables that don't have an inherent order, such as types of animal.                                                                                                     |
| **numeric**       | A data type representing a real decimal number or integer.                                                                                                                            |
| **observation**   | All of the data about a single trial or question.                                                                                                                                     |
| **ordinal**       | Discrete variables that have an inherent order, such as level of education or dislike/like.                                                                                           |
| **outlier**       | A data point that is extremely distant from most of the other data points.                                                                                                            |
| **r markdown**    | The R-specific version of markdown: a way to specify formatting, such as headers, paragraphs, lists, bolding, and links, as well as code blocks and inline code.                      |
| **string**        | A piece of text inside of quotes.                                                                                                                                                     |
| **tidy data**     | A format for data that maps the meaning onto the structure.                                                                                                                           |
| **value**         | A single number or piece of data.                                                                                                                                                     |
| **variable**      | (coding): A word that identifies and stores the value of some data for later use; (stats): An attribute or characteristic of an observation that you can measure, count, or describe. |
| **vector**        | A type of data structure that collects values with the same data type, like T/F values, numbers, or strings.                                                                          |
